Extended Data

### 2022-03-29 doc/manuscript/Dow_manuscript_Nature.Rmd
add some more info on tree-ring methodology

## Tree-ring analysis {-#Tree} 
We analyzed tree-ring records for `r n_cores_sites` sites, including our focal sites.
All cores had been previously collected, cross-dated, and measured using standard collection and processing methodologies[@stokes_introduction_1968].

@@

The tree-ring records from our focal sites were complemented with a much larger collection spanning `r n_cores_sites-2` deciduous and mixed forest sites in eastern North America[@pederson_climatic_2005; @maxwell_sampling_2020;@dorangeville_drought_2018].
Again, records were limited to broadleaf deciduous species with clearly defined xylem porosity (*i.e.*, excluding semi-ring porous).

>>>>

## Tree-ring analysis {-#Tree} 
We analyzed tree-ring records for `r n_cores_sites` sites, including our focal sites.
All cores had been previously collected, cross-dated, and measured using standard collection and processing methodologies[@stokes_introduction_1968;@speer_fundamentals_2010].

@@

The tree-ring records from our focal sites were complemented with a much larger collection spanning `r n_cores_sites-2` deciduous and mixed forest sites in eastern North America[@pederson_climatic_2005;@maxwell_sampling_2020;@dorangeville_drought_2018].
For the majority of sampled populations (i.e., site-species combinations), sampling focused on canopy trees (typically >20 trees per population)[@pederson_climatic_2005;@maxwell_sampling_2020;@dorangeville_drought_2018], while ~15% of the total 207 chronologies came from plot-level collections where trees above a certain diameter (typically 10 cm DBH) were censused and cored[@dye_comparing_2016;@helcoski_growing_2019].
Again, analyses were limited to broadleaf deciduous species with clearly defined xylem porosity (*i.e.*, excluding semi-ring porous).
